Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-25 Paper/Paper.tex
added write up of figure 7

Figure \ref{fig:lle} visualizes the codebook using locally linear
embedding \cite{Roweis2000} to group near neighbors on a 2 dimensional
plane\footnote{We used the implementation from:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}.
This visualization highlights different groups of codewords: sustained
chords on the top left, chord changes on the bottom left, and more
complex sustained chords and ``wideband'' noisy patterns grouping to
the right.

Finally, more related to our particular data, we try to assess how many
sustained patterns are represented in the codebook. We look at
the average variance over time in Figure \ref{fig:code_var}.
25\% of the codebook correspond
to very simple sustained patterns similar to the top row of Figure
\ref{fig:codes1}. For $2$ bars codewords, it seems that patterns
containing more complex temporal activity account for only $33$\% of
the data.

@@

\subsection{Cluster}
Clusters are formed around a centroid (codeword) by all patterns closer
to that codeword than any other. Since the centroid is somewhat an
average of those patterns, the latter tend to be noisier. Hence, codewords
can be seen as the output of a lowpass filtering mecanism.
In Figure \ref{fig:cluster} we show elements of one given
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.

>>>>

An alternate visualization of the codebook is shown in Figure
\ref{fig:lle}.  We use locally linear embedding \cite{Roweis2000} to
group near neighbors on a 2 dimensional plane\footnote{We used the
  implementation from:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}.
This visualization highlights different groups of codewords: sustained
chords on the top left, chord changes on the bottom left, and more
complex sustained chords and ``wideband'' noisy patterns grouping to
the right of the figure.

Given the prevalence of simple codewords in Figures \ref{fig:codes1}
and \ref{fig:lle}, we assess the proportion of the codebook devoted to
representing sustained chord patterns.  The average variance over time
within each codeword is plotted in Figure \ref{fig:code_var}.  From
this figure it is clear that 25\% of the codebook corresponds to very
simple sustained patterns similar to the top row of Figure
\ref{fig:codes1}. For $2$ bar codewords, it seems that patterns
containing more complex temporal activity account for only $33$\% of
the data.

@@

\subsection{Cluster}
Clusters are formed around a centroid (codeword) by all patterns closer
to that codeword than any other. Since the centroid is somewhat an
average of those patterns, the latter tend to be noisier. Hence, codewords
can be seen as the output of a lowpass filtering mechanism.
In Figure \ref{fig:cluster} we show elements of one given
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.
